Optimal (Multiway) Spatial Joins

### 2024-05-19 msj.tex
yufei

SJ is a fundamental operation in spatial databases, which manage geometric entities such as land parcels, service areas, habitat zones, commercial districts, administrative boundaries, etc. It plays a crucial role in implementing the {\em filter-refinement mechanism} \cite{???}, the dominant approach in spatial databases for computing the overlay information of different entities. Specifically, a geometric entity, at the lowest level, is usually modeled as a polygon. Determining whether two entities overlap amounts to deciding if two polygons intersect, which can be very expensive when the polygons have complex boundaries. To alleviate the computation burden, a spatial database stores the {\em minimum bounding rectangle} (MBR) of each polygon $\P$, which is the smallest axis-parallel rectangle enclosing $\P$. Two polygons $\P_1$ and $\P_2$ can overlap with each other only if their MBRs $r_1$ and $r_2$ have a non-empty intersection. Motivated by this, filter-refinement first invokes an SJ

>>>>

SJ is a fundamental operation in spatial databases, which manage geometric entities such as land parcels, service areas, habitat zones, commercial districts, administrative boundaries, etc. It plays a crucial role in implementing the {\em filter-refinement mechanism}, the dominant approach in spatial databases for computing the overlays of different entities. Specifically, a geometric entity, at the lowest level, is usually modeled as a polygon. Determining whether two entities overlap amounts to deciding if two polygons intersect, which can be very expensive when the polygons have complex boundaries. For better efficiency, a spatial database stores the {\em minimum bounding rectangle} (MBR) of each polygon $\P$, which is the smallest axis-parallel rectangle enclosing $\P$. Two polygons $\P_1$ and $\P_2$ can overlap with each other only if their MBRs $r_1$ and $r_2$ have a non-empty intersection. To overlay $k$ different sets of entities, filter-refinement first performs ``filtering'' by using an SJ to fetch all $k$-tuples $(r_1, r_2, ..., r_k)$ where each $r_i$ ($1 \le i \le k$) is the MBR of a polygon $\P_i$ and a ``refines'' every such $k$-tuple by checking if $\P_1, \P_2, ..., \P_k$ indeed have a non-empty intersection.
